Metadata control document

### 2023-06-26 metadata/metadata_control.Rmd
Adding file timestamp back to file metadata

complete_file_data <- bind_rows(samp_filedata, extra_filedata) %>%
  left_join(samp_log)
```

>>>>

if(!file.exists("raw_data/timestamp_filedata.csv")){
  timestamp_filedata <- list.files("../mzMLs", pattern = "mzML", recursive = TRUE, full.names = TRUE) %>%
    RaMS::grabMSdata(grab_what="metadata") %>%
    pluck("metadata") %>%
    distinct(filename, timestamp, polarity) %>%
    mutate(polarity=str_extract(polarity, "..."))

  pooled_patches <- timestamp_filedata %>%
    filter(str_detect(filename, "180821_Poo")) %>%
    distinct(filename, timestamp) %>%
    drop_na()
  timestamp_filedata <- timestamp_filedata %>%
    rows_patch(pooled_patches)
  write_csv(timestamp_filedata, "raw_data/timestamp_filedata.csv")
} else {
  timestamp_filedata <- read_csv("raw_data/timestamp_filedata.csv")
}

complete_file_data <- bind_rows(samp_filedata, extra_filedata) %>%
  left_join(timestamp_filedata, by=c("filename", "polarity")) %>%
  left_join(samp_log)
extra_filedata <- extra_filedata %>%
  left_join(timestamp_filedata)
```
